A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
more on docker

The open nature of the here proposed workflow does blur the lines between published and unpublished.
However, even when your Git repository is public, you may want to signify important stages of your project, like preregistration, preprint, submission and acceptance to the journal.
These milestones deserve to be archived.
A project is only then properly archived when it is stored at least at two independent storage locations and reproducible from all locations.
Therefore, you should make extra sure that the project at these points is reproducible.
To ensure reproducible, you could ask a coworker or collaborator to reproduce the project independently from you.
The sections [Creating a DOI] and [Creating a Release] describe how you can easily create three different openly accessible longterm archived copies of your project.

When you disseminate the paper across more locations than just GitHub it can be ambiguous which version of code and data have created the document (e.g. the manuscript.pdf).
To create a clear link between the repository version and some end result you can automatically include the hash of the commit.
Either you use Git from within R:

```{r}
system2("git", c("rev-parse",  "--short",  "HEAD"), stdout = TRUE)
```

Or you can use the `gert` package:

@@

The approach we advocate for distributes the research project, e.g. across GitHub, preregistration platforms, the publishers site, and more.
Digital Object Identifiers (DOI) tie all these locations together under one link [@derisiWhatWhysDOIs2003].
Not only can a DOI resolve to several locations, several parts of a research project can get their own DOI besides the DOI of the publication.
This is useful to link or cite a specific part of a research project, such as the preregistration, an illustration in the paper or the data that was gathered.
The DOI can also contain information about the license of the object it refers to.
<!-- public releases like preregistration, preprint -->
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artifacts for research and provides doi for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.
You may log into zenodo.org through your GitHub account.

@@

After you have linked a GitHub repository you trigger the archivation by creating a GitHub release, as described in the next section.

@@

A valid point of criticism is that this workflow introduces a bulk of software solutions and services that may not be available for long.
Superficially it relies on R, RStudio, Pandoc, Git, Make, Docker, Homebrew (OS X only) and Chocolaty (Windows only) as software and on GitHub, DockerHub, MRAN and Ubuntu Package Archive as services.
These many breakpoints can be reduced to one service and one software.
That is because all required software is bundled into the container, whose image can be stored.
Hence, one needs a storage provider which saves the container image and the other files associated with the project.
We already recommend to store all project files redundantly (your computer, on GitHub and zenodo.org).
Building the Docker image from the Dockerfile still requires DockerHub, MRAN, and Ubuntu Package Archive to be online.
We therefore suggest that you include an already build image into the releases.
The Makefile generated by `repro` does include a target to facilitate this.
To write a compressed image to disk use:

@@

Unfortunately, this image can only be used when Docker is installed.
To remove any software dependency including Docker from the archived project, one can convert the Docker image to a full system image.
Such system image can subsequently be booted on any personal computer without relying on any software or service and therefore grantees reproducibility for decades to come.
Currently, `repro` does not facilitate this conversion, but we hope to include this feature soon.

>>>>

In a public repository, you may want to mark important stages of your project, like preregistration, preprint, submission and acceptance at a scientific journal.
We suggest to archive these milestones individually.
A reproducible project is only then properly archived when it is stored at least at two independent storage locations and reproducible from all locations. <!--AP citation? -->
To really make sure that a given project is reproducible, one should aim for an explicit test of reproduction before the project is published. 
We recommend to check out and reproduce the project in a new directory in a "fresh" environment (in particular, a new R session should be used for this). 
For maximal validitiy of this test, we suggest to ask a coworker or collaborator to reproduce the project independently from you.
The sections [Creating a DOI] and [Creating a Release] describe how you can easily create three different openly accessible longterm archived copies of your project.

When you disseminate multiple versions of a document (e.g., at different stages of a review process), it seems good practice to specify the exact version of code and data used to create a given document (e.g. the final type-set version of a journal article).
To create a clear link between the repository version and a given end result you can automatically include the unique hash identifying the project state in the git version history.
<!--Either you use Git from within R:

```{r}
system2("git", c("rev-parse",  "--short",  "HEAD"), stdout = TRUE)
```
-->
To this end, we use the `gert` package:

@@

Typical open research project will have their contents available from multiple sites, e.g. from GitHub, preregistration platforms, preprint servers, or publisher websites. 
Under these circumstances it is important to provide unique links 
Digital Object Identifiers (DOI) tie all these locations together under one link [@derisiWhatWhysDOIs2003].
Not only can a DOI resolve to several locations, several parts of a research project can get their own DOI besides the DOI of the publication.
This is useful to link or cite a specific part of a research project, such as the preregistration, an illustration in the paper or the data that was gathered.
The DOI can also contain information about the license of its target.
<!-- public releases like preregistration, preprint -->
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artifacts for research and provides DOIs for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.
You may log into zenodo.org through your GitHub account.

@@

After you have linked a GitHub repository, you trigger the archival by creating a GitHub release, as described in the next section.

@@

A central point of criticism is that the proposed workflow introduces a bulk of software solutions and services that may not be available in the long run.
First and foremost, it relies on R, RStudio, Pandoc, Git, Make, Docker, Homebrew (OS X only) and Chocolaty (Windows only) as software and on GitHub, DockerHub, MRAN and Ubuntu Package Archive as services.
These many breakpoints can be reduced to a single service and a single piece of software.
That is because all required software is bundled into the container, whose image can be stored.
Hence, one needs a storage provider which saves the container image and the other files associated with the project.
We already recommend to store all project files redundantly (your computer, a remote git server such as GitHub, and a publicly funded, open-science-compatible service provider such as zenodo.org).
Building the Docker image from the Dockerfile still requires DockerHub, MRAN, and Ubuntu Package Archive to be online.
We therefore suggest that you include an already built image into the releases.
The Makefile generated by `repro` does include a target to do so.
To write a compressed image to disk use:

@@

This image allows anyone with a computer equipped with Docker to reproduce the analysis (if the repository contains all code and data and has no other external dependencies).
Last, one can convert the Docker image to a full bootable system image.
Such a system image can subsequently be booted on any personal computer without relying on any software or service and therefore grantees reproducibility for decades to come.
Currently, `repro` does not yet facilitate this conversion, but we hope to include this feature soon.
